The influence of resource use on yield versus quality trade-off in Australian vineyards

### 2023-08-17 article.tex
changed to paragraph formating

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield versus quality produced. This dilemma exists across agriculture through shared fundamental considerations such as water use and fuel usage \citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. Quality in viticulture (the cultivation of grapes for wine production) is driven through its integration within the wine industry, with the potential quality of a wine being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability within viticulture is further complicated by environmental and socio-demographic pressures. In the Australian context, these include biosecurity, climate and international market demands.
\newline
\newline
There is an extensive amount of research into the effects of a variety of factors on grape quality and yield \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022,liakosMachineLearningAgriculture2018}. However, due to the lack of long-term and in-depth data, individual factors are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insights at large scales and across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We aim to use this dataset to describe the relationship of resources related to water and fuel use with the output yield and quality of the resultant product, taking into account the size and location of the vineyard. The practical addition of this aim is a baseline for comparison: given a vineyard within Australia, one could estimate the comparative efficiency with regard to the tradeoff between invested resources, yield and quality. This is the first time that such a trade off has been confirmed explicitly across such varying regions, scales and climates in the Australian winegrowing industry.
\section{Methods}
\subsection{Data}

@@

@@

\begin{table}[]
  \caption{Summary statistics of each continuous variable.}\label{tab:summary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cllll@{}}
          \toprule
          \textbf{Variable} & \textbf{Mean} & \textbf{\begin{tabular}[c]{@{}l@{}}Standard\\ Deviation\end{tabular}} & \textbf{Minimum} & \textbf{Maximum} \\ \midrule
          {Yield} & 7.757E+02 & 2.179E+03 & 1.000E+00 & 7.231E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Area Harvested} & 6.670E+05 & 1.337E+06 & 7.000E+02 & 2.436E+07 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Water Used} & 7.471E+06 & 5.646E+08 & 1.000E+00 & 4.268E+10 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Scope One Emissions} & 4.173E+04 & 8.571E+04 & 6.755E+00 & 2.110E+06 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          ${Yield}\over \textbf{Area}$ & 1.009E+01 & 8.127E+00 & 4.000E-02 & 8.634E+01 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Average Sale Price} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          ${Average Sale Price} \over \textbf{Area Harvested}$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule
          \end{tabular}
  }
  \end{table}
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
        \toprule
        \textbf{Variable} & \textbf{Yield} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{Scope One Emissions} & $\textbf{Yield}\over \textbf{Area}$ & \textbf{Average Sale Price} & $\textbf{Average Sale Price}\over \textbf{Area Harvested}$ \\ \midrule
        \textbf{Yield} & 1.00E+00 & 7.44E-01 & -4.31E-03 & 7.29E-01 & 3.50E-01 & -2.26E-01 & -1.64E-01 \\
        \textbf{Area Harvested} & 7.44E-01 & 1.00E+00 & -5.33E-03 & 8.92E-01 & 7.85E-02 & -1.18E-01 & -2.04E-01 \\
        \textbf{Water Used} & -4.31E-03 & -5.33E-03 & 1.00E+00 & -1.93E-03 & -5.60E-03 & -3.56E-02 & -2.67E-02 \\
        \textbf{Scope One Emissions} & 7.29E-01 & 8.92E-01 & -1.93E-03 & 1.00E+00 & 9.36E-02 & -9.42E-02 & -1.93E-01 \\
        $\textbf{Yield}\over \textbf{Area}$ & 3.50E-01 & 7.85E-02 & -5.60E-03 & 9.36E-02 & 1.00E+00 & -4.85E-01 & -1.70E-01 \\
        \textbf{Average Sale Price} & -2.26E-01 & -1.18E-01 & -3.56E-02 & -9.42E-02 & -4.85E-01 & 1.00E+00 & 4.73E-01 \\
        $\textbf{Average Sale Price} \over \textbf{Area Harvested}$ & -1.64E-01 & -2.04E-01 & -2.67E-02 & -1.93E-01 & -1.70E-01 & 4.73E-01 & 1.00E+00 \\ \bottomrule
        \end{tabular}
}
\end{table}
Pearson Correlation Coefficients of the transformed, centered and scaled variables are shown in Table \ref{tab:pearson_correlation}. 
\newline
\newline
All relationships were found to be statistically significant (P $<$ 2.200E-16).
\subsection{General Linear Models}

@@

A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\newline
\newline

@@

\subsection{Limitations}
Limitations in the analyses presented in this paper included overestimating yield for models 1 and 2, and underestimating crop value in models 3 and 4 (see appendix).
% KM: Need to see this.
The issue of model 1 and 2 over-predicting yield may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. More resources were required to prevent these issues from spreading within a region, thus disproportionately affecting some vineyards compared to others locally. This type of maintenance is not well captured in the models, especially when considering that some regions, especially those in warmer areas, are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilised preventative measures in wetter regions, as opposed to those that did not, thus expending less fuel and energy but risking disease. When reviewing the differences between regions, it is important to consider that vineyards in 'Hot Very Dry' areas can be hundreds of times the size of those in other regions. This limitation could be overcome by incorporating the profitability of vineyards, comparing the financial success of working at different operational scales.
\newline
\newline
 %The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
%Reviewing data to uncover reasons for the disparity between production and quality of similar vineyards  included the use of 
Variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost were originally explored to capture the discrepancies between similar vineyards that produced different  yields and crop values. However, none of these variables was significantly correlated with the response variables, and did not add to model accuracy, even when considered as interactions. Allowance for nonlinear relationships, specifically through splines, resulted in more normally distributed residuals but at a drastically reduced overall accuracy when comparing $R^2$ and Residual Square Error. Attempts to fully explain small variations was always overshadowed by the dramatic differences in regional trends.
\newline
\newline
Having more data for each region would also be beneficial, allowing greater comparison between regions. More variables may also help to discern vineyards that can produce larger volumes of grapes at higher prices. The use of other models such as random forests and decision trees alongside more variables and data may help to uncover the reasons for under or overestimation. These differences could be caused by the use of alternative sustainable practices in the field. Moreover, while there is evidence to suggest that environmentally sustainable practices can reduce costs, and increase efficiency whilst improving the quality of grapes; more research is needed to link these benefits across different regions and climates \citep{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.
\section{Conclusion}
% This belongs in the discussion
In summary, vineyard yield and crop value is well-defined by the resources used. However, it is important to consider a vineyard's business goal, region, external pressures and economies of scale where larger vineyards are likely to produce greater overall yields, and have higher yield per area. Smaller vineyards are likely to produce more value per area and a higher quality of grape. It is likely that regional constraints also contribute to the best strategy to pursue when considering quality or quantity.
%KM is this what the data analyses tell you? If so, say so. If not delete.

>>>>

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield versus quality produced. This dilemma exists across agriculture through shared fundamental considerations such as water use and fuel usage \citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. Quality in viticulture (the cultivation of grapes for wine production) is driven through its integration within the wine industry, with the potential quality of a wine being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability within viticulture is further complicated by environmental and socio-demographic pressures. In the Australian context, these include biosecurity, climate and international market demands.
\par
There is an extensive amount of research into the effects of a variety of factors on grape quality and yield \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022,liakosMachineLearningAgriculture2018}. However, due to the lack of long-term and in-depth data, individual factors are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insights at large scales and across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We aim to use this dataset to describe the relationship of resources related to water and fuel use with the output yield and quality of the resultant product, taking into account the size and location of the vineyard. The practical addition of this aim is a baseline for comparison: given a vineyard within Australia, one could estimate the comparative efficiency with regard to the tradeoff between invested resources, yield and quality. This is the first time that such a trade off has been confirmed explicitly across such varying regions, scales and climates in the Australian winegrowing industry.
\section{Methods}
\subsection{Data}

@@

\par

@@

\begin{table}[]
  \caption{Summary statistics of each continuous variable.}\label{tab:summary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cllll@{}}
          \toprule
          \textbf{Variable} & \textbf{Mean} & \textbf{\begin{tabular}[c]{@{}l@{}}Standard\\ Deviation\end{tabular}} & \textbf{Minimum} & \textbf{Maximum} \\ \midrule
          {Yield} & 7.757E+02 & 2.179E+03 & 1.000E+00 & 7.231E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Area Harvested} & 6.670E+05 & 1.337E+06 & 7.000E+02 & 2.436E+07 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Water Used} & 7.471E+06 & 5.646E+08 & 1.000E+00 & 4.268E+10 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Scope One Emissions} & 4.173E+04 & 8.571E+04 & 6.755E+00 & 2.110E+06 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          ${Yield}\over \textbf{Area}$ & 1.009E+01 & 8.127E+00 & 4.000E-02 & 8.634E+01 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Average Sale Price} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          ${Average Sale Price} \over \textbf{Area Harvested}$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule
          \end{tabular}
  }
  \end{table}
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
        \toprule
        \textbf{Variable} & \textbf{Yield} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{Scope One Emissions} & $\textbf{Yield}\over \textbf{Area}$ & \textbf{Average Sale Price} & $\textbf{Average Sale Price}\over \textbf{Area Harvested}$ \\ \midrule
        \textbf{Yield} & 1.00E+00 & 7.44E-01 & -4.31E-03 & 7.29E-01 & 3.50E-01 & -2.26E-01 & -1.64E-01 \\
        \textbf{Area Harvested} & 7.44E-01 & 1.00E+00 & -5.33E-03 & 8.92E-01 & 7.85E-02 & -1.18E-01 & -2.04E-01 \\
        \textbf{Water Used} & -4.31E-03 & -5.33E-03 & 1.00E+00 & -1.93E-03 & -5.60E-03 & -3.56E-02 & -2.67E-02 \\
        \textbf{Scope One Emissions} & 7.29E-01 & 8.92E-01 & -1.93E-03 & 1.00E+00 & 9.36E-02 & -9.42E-02 & -1.93E-01 \\
        $\textbf{Yield}\over \textbf{Area}$ & 3.50E-01 & 7.85E-02 & -5.60E-03 & 9.36E-02 & 1.00E+00 & -4.85E-01 & -1.70E-01 \\
        \textbf{Average Sale Price} & -2.26E-01 & -1.18E-01 & -3.56E-02 & -9.42E-02 & -4.85E-01 & 1.00E+00 & 4.73E-01 \\
        $\textbf{Average Sale Price} \over \textbf{Area Harvested}$ & -1.64E-01 & -2.04E-01 & -2.67E-02 & -1.93E-01 & -1.70E-01 & 4.73E-01 & 1.00E+00 \\ \bottomrule
        \end{tabular}
}
\end{table}
Pearson Correlation Coefficients of the transformed, centered and scaled variables are shown in Table \ref{tab:pearson_correlation}. 
\par
All relationships were found to be statistically significant (P $<$ 2.200E-16).
\subsection{General Linear Models}

@@

A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par

@@

\subsection{Limitations}
Limitations in the analyses presented in this paper included overestimating yield for models 1 and 2, and underestimating crop value in models 3 and 4 (see appendix).
% KM: Need to see this.
The issue of model 1 and 2 over-predicting yield may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. More resources were required to prevent these issues from spreading within a region, thus disproportionately affecting some vineyards compared to others locally. This type of maintenance is not well captured in the models, especially when considering that some regions, especially those in warmer areas, are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilised preventative measures in wetter regions, as opposed to those that did not, thus expending less fuel and energy but risking disease. When reviewing the differences between regions, it is important to consider that vineyards in 'Hot Very Dry' areas can be hundreds of times the size of those in other regions. This limitation could be overcome by incorporating the profitability of vineyards, comparing the financial success of working at different operational scales.
\par
 %The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
%Reviewing data to uncover reasons for the disparity between production and quality of similar vineyards  included the use of 
Variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost were originally explored to capture the discrepancies between similar vineyards that produced different  yields and crop values. However, none of these variables was significantly correlated with the response variables, and did not add to model accuracy, even when considered as interactions. Allowance for nonlinear relationships, specifically through splines, resulted in more normally distributed residuals but at a drastically reduced overall accuracy when comparing $R^2$ and Residual Square Error. Attempts to fully explain small variations was always overshadowed by the dramatic differences in regional trends.
\par
Having more data for each region would also be beneficial, allowing greater comparison between regions. More variables may also help to discern vineyards that can produce larger volumes of grapes at higher prices. The use of other models such as random forests and decision trees alongside more variables and data may help to uncover the reasons for under or overestimation. These differences could be caused by the use of alternative sustainable practices in the field. Moreover, while there is evidence to suggest that environmentally sustainable practices can reduce costs, and increase efficiency whilst improving the quality of grapes; more research is needed to link these benefits across different regions and climates \citep{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.
\section{Conclusion}
% This belongs in the discussion
In summary, vineyard yield and crop value is well-defined by the resources used. However, it is important to consider a vineyard's business goal, region, external pressures and economies of scale where larger vineyards are likely to produce greater overall yields, and have higher yield per area. Smaller vineyards are likely to produce more value per area and a higher quality of grape. It is likely that regional constraints also contribute to the best strategy to pursue when considering quality or quantity.
%KM is this what the data analyses tell you? If so, say so. If not delete.
